Computer Science House By-Laws

### 2016-11-07 bylaws.tex
Spelling, structure, syntax, nonsemantic changes
There were a lot of changes to the original submission so here's a summary:

Generally, I attempted to write the intended proposal in the style of the document.
Split up the sentences a bit more to separate out different parts of the new process.
Referred to the percentage requirement less explicitly, to minimize the risk of future contradiction creation.
Switched simple majority to 50% pass because there should only be two vote options (yes/no).

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
\item Amendment Proposal: If an introductory member fails to meet the requirement of reaching 60\% to get an account after they have completed the two week packet period, the introsuctory member may have the Evals Director bring up a vote at one following house member to give the introductory member an account. This vote may happen once during the introductory member's 10 week evaluation process. The vote is a simple majority vote barring having enough member to meet Quorum
\bsection{Code of Conduct}
The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account. Members may sign a more recent revision of the Code of Conduct to update their agreement.
\bsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}
\end{document}

>>>>

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
	This may occur only once per Introductory Evaluation Process.
\end{enumerate}

\bsection{Code of Conduct}
The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account. Members may sign a more recent revision of the Code of Conduct to update their agreement.
\bsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}
\end{document}
